Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-27 csf2/main.tex
nit

\vspace{-1em}
{
\[
  \begin{array}{rcl}
    %\cca(\src{x}) = &\ \trg{x} 
    % \\
  	%&
  	%\qquad
    %\cca(\src{\lbinop{\expr[_{1}]}{\expr[_{2}]}}) = &\ \lbinop[\trg]{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr[_{2}]})\right]} \\
    %\cca(\src{n}) = &\ \trg{n} 
    % \\
    %&
    \cca(\src{\lget{x}{\expr}}) &= &\ \lget[\trg]{\trg{x}}{\left[\cca(\src{\expr})\right]} \\
    \cca(\src{\ldelete{x}}) &= &\ \ldelete[\trg]{\left[\cca(\src{x})\right]} \\
%    \cca(\src{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = \lset[\trg]{\left[\cca(\src{x})\right]}{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr_{2}})\right]} \\
\cca(\src{\lfunction{g}{x:\natt\to\type[_{e}]}{\expr}})  &= &\ \lfunction[\trg]{\trg{g}}{\trg{x}}{\lifz[\trg]{\trg{\lhast{x}{\natt}}}{
\\%
                                                         &  &
                                                            \left[\cca(\src{\expr})\right] %
                                                                                                 }{\labort[\trg]}}
  \end{array}
\]
}

@@

Action $\trg{Set}$ is treated analogously; any other event is just a trivial re-colouring.\MP{no explicit mentioning of colours. identity functions}
Note that neither $\Ltrg$ nor $\Lms$ expose branches on the trace.\MP{so what?}
The bounds check is left abstract above, since the precise definition needs some technicalities that only inhibit readability without any technical insights.\MP{?? unclear}

@@

>>>>

\vspace{-1em}
{
\begin{gather}
  \begin{align*}%{rcl}
    %\cca(\src{x}) = &\ \trg{x} 
    % \\
  	%&
  	%\qquad
    %\cca(\src{\lbinop{\expr[_{1}]}{\expr[_{2}]}}) = &\ \lbinop[\trg]{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr[_{2}]})\right]} \\
    %\cca(\src{n}) = &\ \trg{n} 
    % \\
    %&
    \cca(\src{\lget{x}{\expr}}) = &\ \lget[\trg]{\trg{x}}{\left[\cca(\src{\expr})\right]} \\
    \cca(\src{\ldelete{x}}) = &\ \ldelete[\trg]{\left[\cca(\src{x})\right]} 
    \\
    \cca(\src{\lfunction{g}{x:\natt\to\type[_{e}]}{\expr}})  =&
  \end{align*}
  \\
  \begin{align*}
%    \cca(\src{\lset{x}{\expr[_{1}]}{\expr[_{2}]}}) & = \lset[\trg]{\left[\cca(\src{x})\right]}{\left[\cca(\src{\expr[_{1}]})\right]}{\left[\cca(\src{\expr_{2}})\right]} \\
% \\ 
\lfunction[\trg]{\trg{g}}{\trg{x}}{\lifz[\trg]{\trg{\lhast{x}{\natt}}}{
                                                            \left[\cca(\src{\expr})\right] %
                                                                                                 }{\labort[\trg]}}
  \end{align*}
\end{gather}
}

@@

Action $\trg{Set}$ is treated analogously; any other event is just a trivial re-colouring.\MPin{no explicit mentioning of colours. identity functions}
% Note that neither $\Ltrg$ nor $\Lms$ expose branches on the trace.\MP{so what?}
For simplicity, we elide the environment that this relation carries around in order to bind each location to its metadata (such as its size), and resolve the ``$\trg{n}$ in/out of bounds'' premise.
% The bounds check mentioned in the premises of the rules above is left abstract for the sake of simplicity, the interested reader can find
% since the precise definition needs some technicalities that only inhibit readability without any technical insights.

@@

\MPin{
	can this be made formal?
	what's the point?
}
